Manuscript Te example

### 2019-11-08 ManuscriptTe.Rmd
Update Te example

```{r}
##Load TrenchR package
library(TrenchR)
```

```{r}
#Grasshopper biophys
library(TrenchR)
library(maptools)
library(ggplot2)

count=function(x){length(na.omit(x))}

error.bars= function(bloc, thing, se, cols="black", ltys="solid"){
  arrows(bloc, thing-se, bloc, thing+se, code=3, angle=90,length=0, col=cols, lty=ltys)
}
#--------------------------
#Grasshopper data
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
spec.dat=read.csv("SpecData.csv")

@@

#------------------------
##Calculate Te for each species
dat$Te<-Tb_grasshopper(T_a=dat$Temp, T_g=dat$SoilTemp, u=dat$Wind, H=dat$Rad, K_t=0.7, psi=dat$psi, L=21.1, Acondfact=0.3)
#fix infinite
dat$Te[is.infinite(dat$Te)]<-NA
#ditch big numbers for now
dat$Te[dat$Te>100]<-NA

#----------------------------------------
#PLOTS

#Subset to August
dat.dt<- strptime(dat$datetime, format="%m/%d/%Y %H:%M", tz="MST") #as.Date
dataug= subset(dat, dat.dt$mon==7)
#subset to day
dataug= subset(dataug, dataug$Rad>5)
#aggregate by day and hour
dat.dh= aggregate(dataug, by=list(dataug$site, dataug$hour), FUN=mean, na.rm=TRUE)

@@

```{r}
library(reshape2)

#convert to long format
dat.s= dat.dh[,c("Rad","Temp","Wind","DodgeiTemp","SoilTemp","SanguinipesTemp","BivatatusTemp","Elev","J", "hour","psi","Te")]

dat.s= melt(dat.s, id = c("Elev", "J","hour","psi"))

#plot
dat.s= subset(dat.s, dat.s %in% c("Temp","SoilTemp","SanguinipesTemp","Te") )

ggplot(data=dat.s, aes(x=hour, y = value, color=variable))+geom_line( ) #+
#  facet_wrap(~Elev)

>>>>

```{r}
##Load TrenchR package
library(TrenchR)
library(maptools)
library(ggplot2)
```

#Microclimate calculations
u_z=function(z, d=0.229, z_0=0.0208, u_star= 0.114, k=0.41) u_star/k*log((z-d)/z_0)

```{r}
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
dat=read.csv("microclimate_C1.csv", sep=",", na.strings = c("-49.99","NA"))
```
```{r}
#ANALYZE SURFACE ROUGHNESS AND PROFILES
C1all$day=  as.POSIXlt(as.character(C1all$datetime),tz='MST', format="%m/%d/%Y %H:%M")$mday
C1all$hour=as.POSIXlt(as.character(C1all$datetime),tz='MST', format="%m/%d/%Y %H:%M")$hour

C1.dayhr<- aggregate(C1all[,c(2:8,13:22)], by=list(C1all$day, C1all$hour), FUN=mean, na.rm=TRUE)
names(C1.dayhr)[1:2]=c("day","hour")
C1.hr<- aggregate(C1all[,c(2:8,13:22)], by=list(C1all$hour), FUN=mean, na.rm=TRUE)
names(C1.hr)[1]="hour"

C1.hr= as.matrix(C1.hr)
#surface roughness
z0= apply(C1.hr[, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], FUN=surface_roughness, MARGIN=1, zr=c(0.25,0.5,1.5,1.5))

z.seq <- seq(0, 2, by = 0.1)

for(hr in 1:24){
t.seq1 <- air_temp_profile_neutral(T_r=C1.hr[hr,"Air0.5m"], zr=0.5, z0=0.02, z=2, T_s=C1.hr[hr,"Soil"])
t.seq2 <- air_temp_profile(T_r=C1.hr[hr,"Air0.5m"], u_r=C1.hr[hr,"Wind0.5m"], zr=0.5, z0=0.02, z=2, T_s=C1.hr[hr,"Soil"])
t.seq3 <- air_temp_profile_segment(T_r=C1.hr[hr, c("Air0.25m","Air0.5m","Air1.0m","Air1.5m")],u_r=C1.hr[hr, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], zr=c(0.25,0.5,1,1.5), z0=0.02, z=2, T_s=C1.hr[hr,"Soil"])

u.seq1<- wind_speed_profile_neutral(u_r=C1.hr[hr,"Wind0.5m"], zr=0.5, z0=0.02, z=2)
u.seq2<- wind_speed_profile(u_r=C1.hr[hr,"Wind0.5m"], zr=0.5, z0=0.02, z=2)
u.seq3<- wind_speed_profile_segment(u_r=C1.hr[hr, c("Wind0.25m","Wind0.5m","Wind1m","Wind1.5m")], zr=c(0.25,0.5,1,1.5), z0=0.02, z=2)
}

#plot(t.seq, z.seq, type = "l", xlab = "Temperature (C)", ylab = "z (height above ground in m)")
```

#Te calculation
```{r}

#Grasshopper data
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
spec.dat=read.csv("SpecData.csv")

@@

#Subset to August
dat.dt<- strptime(dat$datetime, format="%m/%d/%Y %H:%M", tz="MST") #as.Date
dataug= subset(dat, dat.dt$mon==7)
#subset to day
dat= subset(dataug, dataug$Rad>5)

#scale temperature to ground
dat$Tgrass <- air_temp_profile(T_r=dat$Temp, u_r=dat$Wind, zr=0.5, z0=0.02, z=z, T_s=dat$SoilTemp)

#cut nas
dat= dat[,c("Rad","Temp","Wind","SoilTemp","SanguinipesTemp","Elev","J", "hour","psi","Tgrass")]
dat= na.omit(dat)
```

```{r}
##Calculate Te for each species
dat$Te<-Tb_grasshopper(T_a=dat$Tgrass, T_g=dat$SoilTemp, u=dat$Wind, H=dat$Rad, K_t=0.7, psi=dat$psi, L=0.0211, Acondfact=0.01)  #T_a=dat$Tgrass
#fix infinite
dat$Te[is.infinite(dat$Te)]<-NA
#ditch big numbers for now
dat$Te[dat$Te>100]<-NA
```

```{r}
#estimate convective heat transfer coefficient

#Estimate using empirical relationship
dat$H_L=heat_transfer_coefficient(V=dat$Wind,D=0.0211,K=0.025, nu= 15.3 * 10^(-6) , taxa="cylinder")

#Also illustrate estimations using a spherical approximation and a simplified version of the approximation.
H_L1= heat_transfer_coefficient_approximation(V=dat$Wind,D=0.0211,K= 0.025, nu= 15.3 * 10^(-6), taxa="flyinginsect")
H_L2= heat_transfer_coefficient_simple(V=dat$Wind,D=0.0211)

#surface area
A= sa_from_length(l=0.0211)
```

```{r}
#Gates calculation
TeGates= rep(NA, nrow(dat) )

 for(ind in 1:nrow(dat) ){
   out= try(Tb_Gates(A=A, D=0.0211/3, psa_dir=0.66, psa_ref=1-0.66, psa_air=1, psa_g=0.01, T_g=dat$SoilTemp[ind]+273, T_a=dat$Tgrass[ind]+273, Qabs=A*dat$Rad[ind], epsilon=0.95, H_L=dat$H_L[ind], ef=1.3, K=0.15), silent=TRUE)
 if(is.numeric(out))TeGates[ind]=out
 }
  dat$TeGates=TeGates-273.15
```

```{r}
#aggregate by day and hour
dat.dh= suppressWarnings(aggregate(dat, by=list(dat$Elev, dat$hour, dat$J), FUN=mean, na.rm=TRUE))
```

```{r}
#aggregate by hour
dat.h= suppressWarnings(aggregate(dat, by=list(dat$Elev, dat$hour), FUN=mean, na.rm=TRUE))
```

```{r}
library(reshape2)
#convert to long format
dat.s= melt(dat.h, id = c("Elev", "J","hour","psi"))

#plot
dat.s= subset(dat.s, dat.s$variable %in% c("Temp","SoilTemp","SanguinipesTemp","Te","Tgrass","TeGates") )

ggplot(data=dat.s, aes(x=hour, y = value, color=variable))+geom_line(aes(lty=variable) )+facet_wrap(~Elev)

```
```{r}
#plot by date time
dat.dh$Jhr= dat.dh$J +dat.dh$hour/24

#convert to long format
dat.s= melt(dat.dh, id = c("Elev", "J","hour","psi","Jhr"))

#plot
dat.s= subset(dat.s, dat.s$variable %in% c("Temp","SoilTemp","SanguinipesTemp","Te","Tgrass","TeGates") )

plot.t=ggplot(data=dat.s, aes(x=Jhr, y = value, color=variable))+geom_line(aes(lty=variable) )+facet_grid(Elev~1)
```

```{r}
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/figures/")

pdf("TeTime.pdf", height = 10, width = 15)
plot.t
dev.off()

@@
